\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=.75in,right=.75in,bottom=0.6in,top=0.6in, headsep = .4in]{geometry}


\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \large{\textbf{\textsc{\MakeLowercase{#1}}}}}
    \vspace*{-6pt}\lineunder
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0.4pt}


\fancyfoot[C]{\thepage}
\renewcommand{\headrule}{\vspace{-7pt} \hspace{-18pt} \leaders \hrule height \dimexpr 0.4pt \hfill \kern 0pt}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\rhead{\textit{Last Updated: November 23, 2023}}
\lhead{Curriculum Vitae}


\begin{document}

% \vspace*{-40pt}


%==== Profile ====%
 \vspace{50pt}
\begin{center}
	{\Huge \scshape \bfseries {Amaan M. Jogia-Sattar}}\\
 \vspace{2mm}
	Los Angeles, CA $\cdot$ amaanjogiasattar@gmail.com $\cdot$ (818)-447-9553 $\cdot$ https://github.com/amaanjsattar \\
\end{center}

%==== Education ====%
\header{Education}
\vspace{2mm}
\textbf{University of California, Berkeley}\hfill Berkeley, CA\\
B.A. Public Health; Minor: Data Science
\textit{GPA: 3.95} \hfill Aug. 2020 - May 2024\\
\vspace{3mm}

%==== Experience ====%
\header{Research Experience}
\vspace{2mm}

\textbf{UCLA Jonsson Comprehensive Cancer Center} \hfill Los Angeles, CA\\
\textit{Bruins-in-Genomics Summer Undergraduate Researcher, Boutros Lab} \hfill May 2023 - Aug. 2023\\
\vspace{2mm}
\setlength\leftskip{25pt}
\textbf{Advisor: Prof. Paul C. Boutros - Dept. of Human Genetics, Dept. of Urology}\\
\setlength\leftskip{0pt}
\vspace{-2mm}
\begin{itemize} \itemsep 1pt
	\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Objective: Investigating the impact of transcriptional outliers on breast cancer prognosis using RNA-Seq and microarray gene expression data. \item Examined genes exhibiting bimodal sample-wide expression patterns, assessing correlation between outlier gene count and clinical phenotypes. 
 \item Employed multiple Cox regression to assess the predictive role of outlier gene count in patient survival. Performed FDR-corrected univariate Cox modeling to identify extreme outlier genes.  \item Presented findings at the B.I.G. Summer Research Symposium and received Research Excellence Award.
\end{itemize}
\textbf{UC Berkeley Disability Lab} \hfill Berkeley, CA\\
\textit{Lead Undergraduate Researcher / Project Manager: Environmental Sensing} \hfill Sep. 2022 - May 2023\\
\vspace{2mm}
\setlength\leftskip{25pt}
\textbf{Advisor: Prof. Karen Nakamura - Dept. of Anthropology, Chair of Disability Studies}\\
\setlength\leftskip{0pt}
\vspace{-2mm}
\begin{itemize} \itemsep 1pt
	\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
        \item Objective: Identifying the harms of temporal light modulation (TLM) in classroom overhead lighting. 
        \item Led team of 5 researchers in development of sensor with accompanying data-logging interface to quantify frequency variations in classroom lighting.
        \item Analyzed frequency components of logged waveforms using Fourier Transform. Processed component waveform frequencies to calculate stroboscopic visibility measures (SVM) and perceptibility of temporal light modulation (PstLM).
        \item Managed ethnographic outreach to >5,000 disabled and light-sensitive students in partnership with departmental newsletters, student organizations, the Disabled Students Program, and news outlets.

\end{itemize}
\textbf{University of Michigan School of Public Health} \hfill Ann Arbor, MI\\
\textit{Big Data Summer Institute Undergraduate Researcher, Computational HCI Lab} \hfill Jun. 2022 - Jul. 2022\\
\vspace{2mm}
\setlength\leftskip{25pt}
\textbf{Advisor: Prof. Nikola Banovic - Dept. of Electrical Engineering \& Computer Science} \\
\setlength\leftskip{0pt}
\vspace{-2mm}
\begin{itemize}
	\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
    \item Objective: Generating Local Interpretable Model-Agnostic Explanations (LIME) for U-Net multisequence tumour segmentation.
    \item Preprocessed MRI data across T1, T1-gd, T2, and FLAIR sequences. Altered LIME's documentation to accommodate multisequence input.
    \item Reframed segmentation as pixel-wise binary classification task. Leveraged Armis2 HPC cluster to generate composite, explanatory heatmaps for quickshift and felzenszwalb superpixel algorithms.  
    \item Presented findings at the annual Symposium on Big Data, Human Health, and Statistics.

\end{itemize}
\textbf{UC Berkeley Disability Lab} \hfill Berkeley, CA\\
\textit{Undergraduate Researcher: Sensible Computing} \hfill Sep. 2021 - Jun. 2022\\
\vspace{2mm}
\setlength\leftskip{25pt}
\textbf{Advisor: Prof. Karen Nakamura - Dept. of Anthropology, Chair of Disability Studies} \\
\setlength\leftskip{0pt}
\vspace{-2mm}
\begin{itemize}
	\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
    \item Objective: Create a Turing-complete programming environment ideal for learners who find conventional keyboard/mouse/screen programming environments inaccessible.
    \item Prototyped a screenless, tactile-input, programming interface that can be written, read, and debugged through multisensory (tactile, haptic, and auditory) pathways.
    \item Integrated a small, single-board CPU with an attached high-definition camera and OpenCV to enable a running, real-time interpreter for tactile-input code. 
    \item Presented findings at the TrIO-SSS x Berkeley Disability Lab Research Showcase.
\end{itemize}

\vspace{1mm}

%==== Teaching and Mentoring ====%
\header{Teaching \& Mentoring}
\vspace{2mm}

\textbf{UC Berkeley Division of Computing, Data Science, and Society} \hfill Berkeley, CA\\
\textit{Lab Teaching Assistant, Foundations of Data Science} \hfill May 2023 - Aug. 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Assisted 30 students in UC Berkeley's Foundations of Data Science weekly lab introducing computational thinking and statistical inference in Python. 
        \item Taught fundamental data science concepts tested in weekly Jupyter Notebooks, including A/B testing, interpreting confidence, regression, and conditional probability.
\end{itemize}

\vspace{1mm}
%==== Professional Experience ====%
\header{Professional Experience}
\vspace{2mm}

\textbf{UC Berkeley Disability Lab} \hfill Berkeley, CA\\
\textit{Senior Undergraduate Lab Manager} \hfill May 2023 - Aug. 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Directed weekly lab meetings for 20+ undergraduate and graduate researchers.
        \item Facilitated lab access and maintenance for routine meetings and collaborative campus events.
        \item Spearheaded interview and recruitment process for prospective researchers via the Undergraduate Research Apprenticeship Program.
        
\end{itemize}
\textbf{Barnstorm VFX} \hfill Burbank, CA\\
\textit{Operations Research Intern} \hfill Jul 2023 - Aug. 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Managed facility organization- tracking technological inventory, onsite deliveries, and storage efficiency.
        \item Tracked health metrics (temperature, survey responses, etc.) of 20+ onsite employees daily.  Implemented COVID-19 screening initiatives and workplace sanitation protocols.
        \item Conducted attendance screenings and onsite facility management for the company’s 10th-anniversary celebration (approx. 100 attendees).
\end{itemize}

\textbf{University of California, San Diego} \hfill La Jolla, CA\\
\textit{Bioinformatics Mentee} \hfill Jul. 2019\\
\vspace{1mm}
\setlength\leftskip{25pt}

\setlength\leftskip{0pt}
\vspace{-1mm}
\begin{itemize}
	\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
    \item Visualized NCBI sequencing data for genes encoding ABCC-type phytochelatin transporters.
    \item Implemented BLAST to identify sequence similarity and pinpoint mutations enhancing arsenic tolerance in \textit{Arabidopsis thaliana}.
    \item Compared efficacy and efficiency of Illumina Next-Gen SBS Sequencing and Sanger-Chain Termination PCR methods. Discussed
financial and ethical implications in Salk Institute workshops.
\end{itemize}
\vspace{2mm}
%==== Presentations ====%
\header{Presentations}
\vspace{2mm}

\textbf{Oral Presentations}
\begin{itemize}
\item[] 
    \textbf{Jogia-Sattar, A.}, Evans, J., Han, J.Y., Qiu, Z., and Boutros, P.C. (Aug. 2023). \textit{Unveiling Survival Signatures: Assessing Contributions of Transcriptional Outliers on Breast Cancer Survival}. \\
    Boutros Lab Undergraduate Research Showcase, Los Angeles, CA.
    
    \vspace{2mm}
    
    \textbf{Jogia-Sattar, A.}, Nie, R., Kim, A. (Jul. 2022). \textit{Modifying Local Interpretable Model-Agnostic Explanations to Explain Tumour Segmentation Predictions}. \\
    Annual Symposium on Big Data, Human Health, and Statistics, Ann Arbor, MI.
\end{itemize}

\textbf{Poster Presentations}
\begin{itemize}
\item[] 
    \textbf{Jogia-Sattar, A.}, Evans, J., Han, J.Y., Qiu, Z., and Boutros, P.C. (Aug. 2023). \textit{Unveiling Survival Signatures: Assessing Contributions of Transcriptional Outliers on Breast Cancer Survival}. \\
    Poster presented at the UCLA QCBio B.I.G. Summer Research Symposium, Los Angeles, CA.
    
    \vspace{2mm}
    
    Nie, R., \textbf{Jogia-Sattar, A.}, Kim, A. (Nov. 2022). \textit{LIME-S: Explaining Deep Learning-Based Segmentation of Brain Tumour Images}. \\
    Poster presented by coauthor Nie, R. at the 2022 Michigan AI Symposium , Ann Arbor, MI.

     \vspace{2mm}
    
    \textbf{Jogia-Sattar, A.}, Nie, R., Kim, A. (Jul. 2022). \textit{Local Interpretable Model-Agnostic Explanations for Medical Image Segmentation}. \\
    Poster presented at the Annual Symposium on Big Data, Human Health, and Statistics, Ann Arbor, MI.
\end{itemize}
\vspace{2mm}
%==== Honors and Awards ====%
\header{Honors \& Awards}
\vspace{2mm}

\begin{tabular}{@{}l l}
    2023 & Research Excellence Award, \\
         & \textit{UCLA Institute for Quantitative and Computational Biosciences} \\ [4pt]
    2020-2023 & Dean's Honors List (all semesters in attendance) \\
        & \textit{UC Berkeley College of Letters and Sciences} \\ [4pt]
    2020-2023 & Honors to Date (all semesters in attendance) \\
        & \textit{UC Berkeley College of Letters and Sciences} \\ [4pt]
    2021-2022 & Estha M. Rodkey Scholarship, \\
         & \textit{UC Berkeley} \\ [4pt]
    2021-2022 & Berkeley Undergraduate Scholarship, \\
         & \textit{UC Berkeley} \\

\end{tabular}

\vspace{4mm}
%==== Service & Outreach ====%
\header{Campus Involvement \& Outreach}
\vspace{2mm}
\textbf{UC Berkeley Splash - Educational Outreach} \hfill Berkeley, CA \\
\textit{Co-Instructor: Introduction to Disability-Centered Design} \hfill 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Led a high-school seminar critically examining the Principles of Universal Design, their history, and contemporary criticism. Introduced the notion of Disability-Centered Design through a hands-on prototyping exercise. Discussed disability-focused research avenues. 
\end{itemize}

\textbf{Cal Undergraduate Public Health Coalition} \hfill Berkeley, CA\\
\textit{Committee Member: Human Health and Environment (HHE)} \hfill 2021 - 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep1pt
\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Led committee-wide data visualization project examining the relationship between historical redlining and concentration of environmental contaminants in Oakland's water supply. 
        \item Organized Berkeley Public Health faculty presentations and open panels throughout the academic year.
\end{itemize}


\textbf{Mental Health Commission} \hfill Berkeley, CA\\
\textit{Departmental Associate: Associated Students of the University of California (ASUC)} \hfill 2021 - 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Consulted with and organized collaboration between MHC and campus-elected Senators.
        \item Aided organization and launch of UC Berkeley’s Mental Health Week (30+ organizations and 800+ students in attendance).
        \item Facilitated the development of commission-wide podcast and newsletter, including ”Student Spotlight” features and testimonials from licensed mental health professionals.
\end{itemize}


\textbf{RideOn Therapeutic Horsemanship} \hfill Chatsworth, CA\\
\textit{Volunteer Equine Therapy Riding Instructor} \hfill 2020 - 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
\setlength\itemsep{0pt}  % Adjust the spacing between items
	\setlength\parskip{0pt}  % Adjust the spacing between paragraphs
	\setlength\parsep{0pt}  % Adjust the spacing between paragraphs
	\setlength\leftskip{0pt}  % Adjust the indentation
	\renewcommand\labelitemi{\tiny$\bullet$} % Adjust the bullet size
	\item Delivered equine-assisted hippotherapy riding lessons for children and adults with cognitive and physical disabilities.
        \item Collaborated with physical therapists, counselors, and administrators to schedule and format lessons, assist in fundraising, and conduct outreach.
        \item Conducted new volunteer orientiations and trainings on sensitivity, human-animal interaction, and delivery of instruction.
\end{itemize}

\end{document}